\subsection{Datasets}
\subsubsection{Synthetic Scene}

Manually created synthetic scene with geometric primitives.
This shows the effect of translation and rotation on the provided feature images.
Furthermore, it is the basis to judge the feasability of the different feature images.

\subsubsection{Lehrpfad Kinect}

Kinectv2-data from a robot drive in the Reiche Zeche.
It provides groundthruth data from a prior reconstruction after global optimization.
It contains a loop closure and different section of the mining environment, from man made concrete walls to raw stone walls.
The groundthruth poses do not match the scale of the depth sensor anymore, as global optimization adjusted the translation too much.
The rotation is proper, each pose is adjusted with ICP that uses the provided pose as initial guess.

\subsubsection{Office Kinect}



\subsubsection{Laserscans of Reiche Zeche - Wilhelm Stehender Süd}

LIDAR based high resolution scans that are used in the context of mine surveying.
Those scans are not made for robotic or computer vision purposes.
This is the reason, why they have little overlap between each scan.
Special reflectors are used as landmarks to register the point clouds to each other.
Only a subset of the scans is used in this evaluation, to demonstrate the functionality and generality of the approach.
Statistics of the distribution and response of the keypoints are provided.

\subsubsection{LIDAR and Pinhole Camera matching}

One advantage of the feature based approach is mixing highly different depth sensors with ease.
Examplaric scene with data from Kinectv2 sensor and the LIDAR that demonstrates, that matching between those two sensors is possible.
Demonstrate, that prior conversion from equirectangular to pinhole reduces the distortion and therefore change in appearance between different camera models.

% Lehrpfad Ziege ist auch im Wilhelm-Sued-Kinect Datensatz. Damit ist da Equi, +Laserscan Pinhole + Kinect vorhanden

\subsubsection{Synthetic City Scene}

City walkthrough that is used as odometry benchmark.

